---
title: "The Psychology of Climate Change Communication"
subtitle: "Theoretical insights and practical applications<br>{{< var university.name >}} · {{< var course.semester >}} · {{< var course.weekday >}} {{< var course.start >}}–{{< var course.end >}} · room {{< var course.room >}}"
toc: false
resources:
  - course-sessions.ics
---

## Instructors

{{< fa user >}} [{{< var instructors.viktoria.name >}}]({{< var instructors.viktoria.url >}}) \| {{< fa envelope >}} <a href='mailto:{{< var instructors.viktoria.email >}}'>{{< var instructors.viktoria.email >}}</a><br>
{{< fa user >}} [{{< var instructors.jan.name >}}]({{< var instructors.jan.url >}}) \| {{< fa envelope >}} <a href='mailto:{{< var instructors.jan.email >}}'>{{< var instructors.jan.email >}}</a> \| {{< iconify fa6-brands bluesky size=1.1em title='Bluesky' >}} [Bluesky]({{< var instructors.jan.bluesky >}})

## Course Description

Climate change communication influences how individuals, organizations, and societies perceive climate change, and how they react to it. In this course, we will discuss research findings in environmental psychology and communication science to understand specific challenges of climate change communication and how to address them.

## Schedule

Session topics below are a draft carried over from a previous version of the course and will be revised. Full session descriptions and readings are in the [syllabus](syllabus.qmd).

{{< fa calendar >}} [Download all sessions as a calendar file (.ics)](course-sessions.ics)

```{r}
#| echo: false
#| message: false
#| warning: false
library(tinytable)
# Single sources: the .session divs in syllabus.qmd (topics, lecturers,
# literature — authored there so citation keys autocomplete in Positron) and
# _variables.yml (weekday, times, room, first_session). Session dates are
# first_session + 7 days per session, unless a div sets an explicit
# date="dd.mm.yyyy" override.
vars <- yaml::read_yaml("_variables.yml")
lines <- readLines("syllabus.qmd", warn = FALSE)
sess <- grep('\\{\\.session ', lines, value = TRUE)
attr_of <- function(x, name) {
  ifelse(grepl(paste0(" ", name, '="'), x),
         sub(paste0('.*', name, '="([^"]*)".*'), "\\1", x),
         NA_character_)
}
n <- as.integer(attr_of(sess, "number"))
computed <- format(as.Date(vars$course$first_session) + (n - 1) * 7, "%d.%m.%Y")
date_override <- attr_of(sess, "date")
overview <- data.frame(
  n = n,
  Date = ifelse(is.na(date_override), computed, date_override),
  Topic = attr_of(sess, "topic"),
  Lecturer = attr_of(sess, "lecturer")
)
names(overview)[1] <- "#"
tt(overview, width = c(0.05, 0.15, 0.52, 0.28))
```

```{r}
#| label: write-ics
#| include: false
# Calendar file with one event per session, downloadable from the link above.
# Times use TZID so the late-October clock change does not shift the sessions.
esc <- function(x) gsub("([\\\\;,])", "\\\\\\1", x)
fold <- function(lines) {
  unlist(lapply(lines, function(l) {
    out <- character(0)
    while (nchar(l) > 73) {
      out <- c(out, substr(l, 1, 73))
      l <- paste0(" ", substr(l, 74, nchar(l)))
    }
    c(out, l)
  }))
}
tz <- vars$course$timezone
dates_iso <- format(as.Date(overview$Date, "%d.%m.%Y"), "%Y%m%d")
start_t <- paste0(gsub(":", "", vars$course$start), "00")
end_t <- paste0(gsub(":", "", vars$course$end), "00")
loc <- paste0(vars$university$name, ", ", vars$course$room)
stamp <- paste0(format(as.Date(vars$course$first_session), "%Y%m%d"), "T000000Z")
events <- unlist(lapply(seq_along(n), function(i) c(
  "BEGIN:VEVENT",
  sprintf("UID:session-%02d@course-climate-communication", n[i]),
  paste0("DTSTAMP:", stamp),
  paste0("DTSTART;TZID=", tz, ":", dates_iso[i], "T", start_t),
  paste0("DTEND;TZID=", tz, ":", dates_iso[i], "T", end_t),
  paste0("SUMMARY:", esc(paste0("Climate Communication ", n[i], ": ", overview$Topic[i]))),
  paste0("LOCATION:", esc(loc)),
  paste0("DESCRIPTION:", esc(paste0("Lecturer: ", overview$Lecturer[i]))),
  "END:VEVENT"
)))
# Central European daylight-saving rules (last Sunday of March / October)
vtimezone <- c(
  "BEGIN:VTIMEZONE",
  paste0("TZID:", tz),
  "BEGIN:DAYLIGHT",
  "TZOFFSETFROM:+0100", "TZOFFSETTO:+0200", "TZNAME:CEST",
  "DTSTART:19700329T020000", "RRULE:FREQ=YEARLY;BYMONTH=3;BYDAY=-1SU",
  "END:DAYLIGHT",
  "BEGIN:STANDARD",
  "TZOFFSETFROM:+0200", "TZOFFSETTO:+0100", "TZNAME:CET",
  "DTSTART:19701025T030000", "RRULE:FREQ=YEARLY;BYMONTH=10;BYDAY=-1SU",
  "END:STANDARD",
  "END:VTIMEZONE"
)
ics <- c(
  "BEGIN:VCALENDAR",
  "VERSION:2.0",
  "PRODID:-//course_climate_communication//EN",
  "CALSCALE:GREGORIAN",
  "X-WR-CALNAME:The Psychology of Climate Change Communication",
  vtimezone,
  events,
  "END:VCALENDAR"
)
writeLines(fold(ics), "course-sessions.ics", sep = "\r\n")
```
