---
title: "The Psychology of Climate Change Communication"
subtitle: "Theoretical insights and practical applications<br>{{< var university.name >}} · {{< var course.semester >}} · {{< var course.weekday >}} {{< var course.start >}}–{{< var course.end >}} · room {{< var course.room >}}"
toc: false
resources:
  - course-sessions.ics
---

## Instructors

{{< fa user >}} [{{< var instructors.viktoria.name >}}]({{< var instructors.viktoria.url >}}) \| {{< fa envelope >}} <a href='mailto:{{< var instructors.viktoria.email >}}'>{{< var instructors.viktoria.email >}}</a><br>
{{< fa user >}} [{{< var instructors.jan.name >}}]({{< var instructors.jan.url >}}) \| {{< fa envelope >}} <a href='mailto:{{< var instructors.jan.email >}}'>{{< var instructors.jan.email >}}</a> \

## Course Description

Climate change communication influences how individuals, organizations, and societies perceive climate change, and how they react to it. In this course, we will discuss research findings in environmental psychology and communication science to understand specific challenges of climate change communication and how to address them.

## Schedule

Guest speaker descriptions and some readings are still being finalized. Full session descriptions and readings are in the [syllabus](syllabus.qmd).

::: {.calendar-box}
**{{< fa calendar >}} Course calendar** — get all sessions into your calendar app.

[{{< fa calendar-plus >}} Subscribe](webcal://janpfander.github.io/course_climate_communication/course-sessions.ics){.btn .btn-primary .btn-sm} [{{< fa download >}} Download .ics](course-sessions.ics){.btn .btn-outline-primary .btn-sm}

::: {.calendar-note}
Subscribing keeps the events up to date when the schedule changes. A downloaded copy will not receive later changes. In Google Calendar, subscribe via *Settings → Add calendar → From URL* with `https://janpfander.github.io/course_climate_communication/course-sessions.ics`.
:::
:::

```{r}
#| echo: false
#| message: false
#| warning: false
library(tinytable)
# Single sources: the .session divs in syllabus.qmd (topics, lecturers,
# literature — authored there so citation keys autocomplete in Positron) and
# _variables.yml (weekday, times, room, first_session). Session dates are
# first_session + 7 days per session, unless a div sets an explicit
# date="dd.mm.yyyy" override.
vars <- yaml::read_yaml("_variables.yml")
lines <- readLines("syllabus.qmd", warn = FALSE)
sess <- grep('\\{\\.session ', lines, value = TRUE)
attr_of <- function(x, name) {
  ifelse(grepl(paste0(" ", name, '="'), x),
         sub(paste0('.*', name, '="([^"]*)".*'), "\\1", x),
         NA_character_)
}
n <- as.integer(attr_of(sess, "number"))
computed <- format(as.Date(vars$course$first_session) + (n - 1) * 7, "%d.%m.%Y")
date_override <- attr_of(sess, "date")
overview <- data.frame(
  n = n,
  Date = ifelse(is.na(date_override), computed, date_override),
  Topic = attr_of(sess, "topic"),
  Lecturer = attr_of(sess, "lecturer")
)
names(overview)[1] <- "#"
tt(overview, width = c(0.05, 0.15, 0.52, 0.28))
```

```{r}
#| label: write-ics
#| include: false
# Calendar file with one event per session, downloadable from the link above.
# Times use TZID so the late-October clock change does not shift the sessions.
esc <- function(x) gsub("([\\\\;,])", "\\\\\\1", x)
fold <- function(lines) {
  unlist(lapply(lines, function(l) {
    out <- character(0)
    while (nchar(l) > 73) {
      out <- c(out, substr(l, 1, 73))
      l <- paste0(" ", substr(l, 74, nchar(l)))
    }
    c(out, l)
  }))
}
tz <- vars$course$timezone
dates_iso <- format(as.Date(overview$Date, "%d.%m.%Y"), "%Y%m%d")
start_t <- paste0(gsub(":", "", vars$course$start), "00")
end_t <- paste0(gsub(":", "", vars$course$end), "00")
loc <- paste0(vars$university$name, ", ", vars$course$room)
# DTSTAMP/LAST-MODIFIED = render time and SEQUENCE = number of commits that
# touched syllabus.qmd, so subscribed calendars treat every schedule change as
# an update (some clients ignore edits when these fields do not change).
stamp <- format(Sys.time(), "%Y%m%dT%H%M%SZ", tz = "UTC")
seq_n <- suppressWarnings(as.integer(system("git rev-list --count HEAD -- syllabus.qmd", intern = TRUE)))
if (length(seq_n) != 1 || is.na(seq_n)) seq_n <- 0L
events <- unlist(lapply(seq_along(n), function(i) c(
  "BEGIN:VEVENT",
  sprintf("UID:session-%02d@course-climate-communication", n[i]),
  paste0("DTSTAMP:", stamp),
  paste0("LAST-MODIFIED:", stamp),
  paste0("SEQUENCE:", seq_n),
  paste0("DTSTART;TZID=", tz, ":", dates_iso[i], "T", start_t),
  paste0("DTEND;TZID=", tz, ":", dates_iso[i], "T", end_t),
  paste0("SUMMARY:", esc(paste0("Climate Communication ", n[i], ": ", overview$Topic[i]))),
  paste0("LOCATION:", esc(loc)),
  paste0("DESCRIPTION:", esc(paste0("Lecturer: ", overview$Lecturer[i]))),
  "END:VEVENT"
)))
# Central European daylight-saving rules (last Sunday of March / October)
vtimezone <- c(
  "BEGIN:VTIMEZONE",
  paste0("TZID:", tz),
  "BEGIN:DAYLIGHT",
  "TZOFFSETFROM:+0100", "TZOFFSETTO:+0200", "TZNAME:CEST",
  "DTSTART:19700329T020000", "RRULE:FREQ=YEARLY;BYMONTH=3;BYDAY=-1SU",
  "END:DAYLIGHT",
  "BEGIN:STANDARD",
  "TZOFFSETFROM:+0200", "TZOFFSETTO:+0100", "TZNAME:CET",
  "DTSTART:19701025T030000", "RRULE:FREQ=YEARLY;BYMONTH=10;BYDAY=-1SU",
  "END:STANDARD",
  "END:VTIMEZONE"
)
ics <- c(
  "BEGIN:VCALENDAR",
  "VERSION:2.0",
  "PRODID:-//course_climate_communication//EN",
  "CALSCALE:GREGORIAN",
  "X-WR-CALNAME:The Psychology of Climate Change Communication",
  "X-PUBLISHED-TTL:PT12H",
  "REFRESH-INTERVAL;VALUE=DURATION:PT12H",
  vtimezone,
  events,
  "END:VCALENDAR"
)
writeLines(fold(ics), "course-sessions.ics", sep = "\r\n")
```
